Reasoning About a Machine with Local Capabilities

### 2019-02-10 toplas/paper.tex
[TOPLAS] Add notes, update TODO and fix reference
[TOPLAS] Add CHERI reference for stack smashing

The final question that remains is: where should we store this activation
record? The attentive reader may already see that there is only one possibility:
since the activation record contains the old stack pointer, which is local, the
activation record can only be constructed in a part of memory where we have
write-local access, i.e.\ on the stack. Note that this means we will be placing
and executing instructions on the stack, i.e.\ it will not just contain code
pointers and data. This means that our calling convention should be combined
with protection against stack smashing attacks (i.e.\ buffer overflows on the
stack overwriting activation records' contents). Luckily, the capability
machine's fine-grained memory protection should make it reasonably easy for a
compiler to implement such protection by making sure that only appropriately
bounded versions of the stack pointer are made available to source language
code.

@@

>>>>

The final question that remains is: where should we store this activation
record? The attentive reader may already see that there is only one possibility:
since the activation record contains the old stack pointer, which is local, the
activation record can only be constructed in a part of memory where we have
write-local access, i.e.\ on the stack. Note that this means we will be placing
and executing instructions on the stack, i.e.\ it will not just contain code
pointers and data. This means that our calling convention should be combined
with protection against stack smashing attacks (i.e.\ buffer overflows on the
stack overwriting activation records' contents). Luckily, the capability
machine's fine-grained memory protection \citep{Woodruff:2014:CCM:2665671.2665740} should make it reasonably easy for a
compiler to implement such protection by making sure that only appropriately
bounded versions of the stack pointer are made available to source language
code.

@@

% \citet{skorstengaard_stktokens_2019} gives a definition of well-bracketed control flow based on overlay semantics.
% Their definition characterizes the kind of well-bracketed control flow our examples rely on.
% They define well-bracketed control flow for a capability machine by defining a new machine that is syntactically the same but adds a built-in call stack that is only accessed when a series of instructions corresponding to a call or return is executed.
